---
title: "Enviro DIY - Crosslands Demo"
author: "LimnoTech"
date: "August 24, 2017"
output: 
  html_document:
    theme: cosmo
    highlight: tango
    toc: true
    toc_float: true
runtime: shiny

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(ggplot2)
library(tidyverse)
library(quantmod)
library(shiny)
library(ggiraph)
library(plotly)
library(WaterML)
library(leaflet)

```





#Site Location

**LimnoTech** has installed an EnviroDIY site in a stormwater pond on Crosslands property. The surface area of the pond is approximately XX square feet and receives runof from approximately XX square feet of rooftop and parking lots. 

```{r echo=FALSE, warning=FALSE, include=FALSE}

server <- "http://odm2wofpy.uwrl.usu.edu:8080/odm2timeseries/soap/cuahsi_1_0/.wsdl"
info <- GetSiteInfo(server, "odm2timeseries:160065_Crosslands")
lat <- info$Latitude[1]
long <- info$Longitude[1]
sitename <- info$SiteName[1]


```


```{r echo=FALSE, warning = FALSE}

marker1 <- paste0("<strong>Site Name: </strong>", info$SiteName, "<dd>", "<strong>Number of Variables: </strong>", dim(info)[1], "<dd>", "<strong>Organization: </strong>", info$organization)


output$map <- renderLeaflet({
  map <- leaflet() %>%
    addProviderTiles("CartoDB.Positron", group= "Light Basemap") %>%
    addTiles(urlTemplate = 'http://{s}.google.com/vt/lyrs=s&x={x}&y={y}&z={z}',
       attribution = 'Data source: Map data: Google, DigitalGlobe</a>', 
       options = tileOptions(maxZoom = 20, minZoom=9, subdomains=c("mt0", "mt1", "mt2", "mt3")), group="Aerial Imagery") %>%
    setView(lng = long, lat = lat, zoom=15) %>%
    addMarkers(info$Longitude[1],info$Latitude[1], popup= marker1, label=info$SiteName) %>%
    addLayersControl(
      overlayGroups = c("Aerial Imagery"), 
      options = layersControlOptions(collapsed = FALSE)) %>%
    hideGroup(c("Aerial Imagery"))
})

leafletOutput('map')

``` 


#Site Info
***Board:*** Mayfly v0.5 <br>
***Variables:***


#Live Data Summary

```{r include=FALSE}



```


```{r echo=FALSE, warning = FALSE}

vars <- c('Depth', 'Board Temperature', 'Air Temperature', 'Water Temperature')

inputPanel(

    column(12,
          h4("Variable"),
          selectizeInput("Var", "", vars, options = list(
          placeholder='Please select',
          onInitialize = I('function() {this.setValue(""); }')
          ))
    )
)


```




```{r echo=FALSE, warning = FALSE}

renderPlotly({
  if(input$Var == "Depth"){
    wdepth <- GetValues(server, siteCode="odm2timeseries:160065_Crosslands", variableCode="odm2timeseries:MaxBotix_MB7386_Distance")
    tidy <- separate(wdepth, time, into=c("date", "time"), sep="T")
    tidy$datetime <- paste(tidy$date, " ", tidy$time,sep="")
    tidy$datetime <- as.POSIXct(strptime(tidy$datetime,format="%Y-%m-%d %H:%M:%S"))
    tidy$date <- as.POSIXct(strptime(tidy$date, format="%Y-%m-%d"))
    wdepth$datetime <- tidy$datetime
    wdepth$date <- tidy$date
    wdepth <- wdepth %>% filter(DataValue != 0)
    wdepth <- wdepth %>% filter(DataValue != 9999)
    wdepth <- wdepth %>% filter(DataValue < 4000) 
    wdepth$Depth = 4000 - wdepth$DataValue
    wdepth_dmax <- wdepth %>% group_by(date) %>% summarise(maxDepth=max(Depth))
    mindate <- min(wdepth_dmax$date)
    maxdate <- max(wdepth_dmax$date)
    range <- data.frame(date=seq.POSIXt(mindate, maxdate, by=86400))
    wdepth_dmax <- left_join(range, wdepth_dmax, by="date")
    wdepth_dmax$ribmin <- 0
    wdepth_dmax <- wdepth_dmax %>% mutate(ribmax = ifelse(is.na(maxDepth),0,maxDepth))

    p <- ggplot(wdepth_dmax,aes(x=date, y=maxDepth)) + 
            geom_line(colour="steelblue") +
            geom_ribbon(aes(x=date, ymin=ribmin, ymax=ribmax), fill="steelblue", alpha = 0.5) +
            theme_minimal() + 
            theme(panel.background = element_rect(colour=NA, fill="grey97")) + 
            xlab("Date") + 
            ylab("Water Depth (mm)")
    plotly_p <- ggplotly(p, dynamicTicks=TRUE)
    plotly_p
  }
})

renderTable({
  if(input$Var == "Depth"){
    wdepth <- GetValues(server, siteCode="odm2timeseries:160065_Crosslands", variableCode="odm2timeseries:MaxBotix_MB7386_Distance")
    tidy <- separate(wdepth, time, into=c("date", "time"), sep="T")
    tidy$datetime <- paste(tidy$date, " ", tidy$time,sep="")
    tidy$datetime <- as.POSIXct(strptime(tidy$datetime,format="%Y-%m-%d %H:%M:%S"))
    tidy$date <- as.POSIXct(strptime(tidy$date, format="%Y-%m-%d"))
    wdepth$datetime <- tidy$datetime
    wdepth$date <- tidy$date
    wdepth <- wdepth %>% filter(DataValue != 0)
    wdepth <- wdepth %>% filter(DataValue != 9999)
    wdepth <- wdepth %>% filter(DataValue < 4000) 
    wdepth$Depth = 4000 - wdepth$DataValue
    wdepth_dmax <- wdepth %>% group_by(date) %>% summarise(maxDepth=max(Depth))
    mindate <- min(wdepth_dmax$date)
    maxdate <- max(wdepth_dmax$date)
    range <- data.frame(date=seq.POSIXt(mindate, maxdate, by=86400))
    wdepth_dmax <- left_join(range, wdepth_dmax, by="date")
    wdepth_dmax$ribmin <- 0
    wdepth_dmax$ribmax <- ifelse(wdepth_dmax$maxDepth>0,wdepth_dmax$maxDepth, 0)

    wdepth_dmax
  }
})















